Iterative Monomorphisation

### 2024-01-29 iterative_monomorphisation.tex
continued working on tables

\begin{table}[H]
\caption{Monomorphic type argument generation}
\centering\begin{tabular}{@{}llc*{9}{>{\centering\arraybackslash}p{1.5em}}@{}}
   && \multicolumn{3}{c}{floor 1} & \multicolumn{3}{c}{floor 3} & \multicolumn{3}{c}{floor 9}\\
   \cmidrule(lr){3-5} \cmidrule(lr){6-8} \cmidrule(lr){9-11}
   && \multicolumn{3}{c}{multiplier} & \multicolumn{3}{c}{multiplier} & \multicolumn{3}{c}{multiplier}\\
   && 0.0 & 1.0 & 2.0 & 0.0 & 1.0 & 2.0 & 0.0 & 1.0 & 2.0\\
   \cmidrule(lr){3-5} \cmidrule(lr){6-8} \cmidrule(lr){9-11}
   \multirow{4}{1em}{cap}
   & \multicolumn{1}{l|}{25} & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
   & \multicolumn{1}{l|}{50} & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
   &\multicolumn{1}{l|}{100} & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
   &\multicolumn{1}{l|}{none}& 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
\end{tabular}
\end{table}

@@

\begin{table}[H]
\caption{Polymorphic type argument generation}
\centering\begin{tabular}{@{}llc*{9}{>{\centering\arraybackslash}p{1.5em}}@{}}
   && \multicolumn{3}{c}{floor 0} & \multicolumn{3}{c}{floor 3} & \multicolumn{3}{c}{floor 6}\\
   \cmidrule(lr){3-5} \cmidrule(lr){6-8} \cmidrule(lr){9-11}
   && \multicolumn{3}{c}{multiplier} & \multicolumn{3}{c}{multiplier} & \multicolumn{3}{c}{multiplier}\\
   && 0.0 & 0.5 & 1.0 & 0.0 & 0.5 & 1.0 & 0.0 & 0.5 & 1.0\\
   \cmidrule(lr){3-5} \cmidrule(lr){6-8} \cmidrule(lr){9-11}
   \multirow{4}{1em}{cap}
   & \multicolumn{1}{l|}{10} & \multirow{4}{1em}{0} & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
   & \multicolumn{1}{l|}{20}  && 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
   &\multicolumn{1}{l|}{50}  && 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
   &\multicolumn{1}{l|}{none} && 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
\end{tabular}
\end{table}

@@

The choice to also include e-timeout in this table is due to the fact that E being successful in solving a monomorphised problem in a certain time limit is highly dependent on the number of clauses it is given.

\begin{table}[H]
\caption{Clause generation}
\centering\begin{tabular}{@{}llc*{9}{>{\centering\arraybackslash}p{1.5em}}@{}}
   && \multicolumn{3}{c}{500 cap} & \multicolumn{3}{c}{2000 cap} & \multicolumn{3}{c}{no cap}\\
   \cmidrule(lr){3-5} \cmidrule(lr){6-8} \cmidrule(lr){9-11}
   && \multicolumn{3}{c}{multiplier} & \multicolumn{3}{c}{multiplier} & \multicolumn{3}{c}{multiplier}\\
   && 1.0 & 2.0 & 3.0 & 1.0 & 2.0 & 3.0 & 1.0 & 2.0 & 3.0\\
   \cmidrule(lr){3-5} \cmidrule(lr){6-8} \cmidrule(lr){9-11}
   \multirow{4}{4.2em}{e-timeout}
   & \multicolumn{1}{l|}{1 s} & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
   & \multicolumn{1}{l|}{5 s} & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
   &\multicolumn{1}{l|}{10 s} & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
   &\multicolumn{1}{l|}{none} & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
\end{tabular}
\end{table}

\begin{table}[H]
\caption{Substitution generation}
\centering\begin{tabular}{@{}llc*{4}{>{\centering\arraybackslash}p{1.5em}}@{}}
   \toprule
   & & \multicolumn{4}{c}{mono subst per clause}\\
   & & 2 & 5 & 7 & 10\\
   \cmidrule(lr){3-6}
   \multirow{4}{4.1em}{subst cap}
   & \multicolumn{1}{l|}{50}   & 0 & 0 & 0 & 0\\
   & \multicolumn{1}{l|}{100}  & 0 & 0 & 0 & 0\\
   & \multicolumn{1}{l|}{500}  & 0 & 0 & 0 & 0\\
   & \multicolumn{1}{l|}{none} & 0 & 0 & 0 & 0\\

@@

\begin{table}[H]
\caption{Substitution generation}
\centering\begin{tabular}{@{}llc*{4}{>{\centering\arraybackslash}p{1.5em}}@{}}
   \toprule
   & & \multicolumn{4}{c}{e call step}\\
   & & 0 & 15 & 45 & 90\\
   \cmidrule(lr){3-6}
   \multirow{4}{3.3em}{loop nb}
   & \multicolumn{1}{l|}{2} & 0 & 0 & 0 & 0\\
   & \multicolumn{1}{l|}{3} & 0 & 0 & 0 & 0\\
   & \multicolumn{1}{l|}{4} & 0 & 0 & 0 & 0\\
   & \multicolumn{1}{l|}{5} & 0 & 0 & 0 & 0\\

@@

>>>>

\begin{table}[H]
\caption{Monomorphic type argument generation}
\centering\begin{tabular}{@{}llc*{9}{>{\centering\arraybackslash}p{1.5em}}@{}}
   && \multicolumn{3}{c}{floor 1} & \multicolumn{3}{c}{floor 3} & \multicolumn{3}{c}{floor 9}\\
   \cmidrule(lr){3-5} \cmidrule(lr){6-8} \cmidrule(lr){9-11}
   && \multicolumn{3}{c}{multiplier} & \multicolumn{3}{c}{multiplier} & \multicolumn{3}{c}{multiplier}\\
   && 0.0 & 1.0 & 2.0 & 0.0 & 1.0 & 2.0 & 0.0 & 1.0 & 2.0\\
   \cmidrule(lr){3-5} \cmidrule(lr){6-8} \cmidrule(lr){9-11}
   \multirow{4}{1.5em}{cap}
   & \multicolumn{1}{l|}{25}   & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
   & \multicolumn{1}{l|}{50}   & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
   & \multicolumn{1}{l|}{100}  & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
   & \multicolumn{1}{l|}{none} & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
\end{tabular}
\end{table}

@@

\begin{table}[H]
\caption{Polymorphic type argument generation}
\centering\begin{tabular}{@{}llc*{9}{>{\centering\arraybackslash}p{1.5em}}@{}}
   && \multicolumn{3}{c}{floor 0} & \multicolumn{3}{c}{floor 3} & \multicolumn{3}{c}{floor 6}\\
   \cmidrule(lr){3-5} \cmidrule(lr){6-8} \cmidrule(lr){9-11}
   && \multicolumn{3}{c}{multiplier} & \multicolumn{3}{c}{multiplier} & \multicolumn{3}{c}{multiplier}\\
   && 0.0 & 0.5 & 1.0 & 0.0 & 0.5 & 1.0 & 0.0 & 0.5 & 1.0\\
   \cmidrule(lr){3-5} \cmidrule(lr){6-8} \cmidrule(lr){9-11}
   \multirow{4}{1.5em}{cap}
   & \multicolumn{1}{l|}{10} 
   & \multirow{4}{1em}{0}       & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
   & \multicolumn{1}{l|}{20}   && 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
   & \multicolumn{1}{l|}{50}   && 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
   & \multicolumn{1}{l|}{none} && 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
\end{tabular}
\end{table}

@@

The choice to also include e-timeout in this table is due to the fact that E being successful in solving a monomorphised problem in a certain time limit has been observed to be highly dependent on the number of clauses it is given.

\begin{table}[H]
\caption{Clause generation}
\centering\begin{tabular}{@{}llc*{9}{>{\centering\arraybackslash}p{1.5em}}@{}}
   && \multicolumn{3}{c}{500 cap} & \multicolumn{3}{c}{2000 cap} & \multicolumn{3}{c}{no cap}\\
   \cmidrule(lr){3-5} \cmidrule(lr){6-8} \cmidrule(lr){9-11}
   && \multicolumn{3}{c}{multiplier} & \multicolumn{3}{c}{multiplier} & \multicolumn{3}{c}{multiplier}\\
   && 1.0 & 2.0 & 3.0 & 1.0 & 2.0 & 3.0 & 1.0 & 2.0 & 3.0\\
   \cmidrule(lr){3-5} \cmidrule(lr){6-8} \cmidrule(lr){9-11}
   \multirow{4}{4.2em}{e-timeout}
   & \multicolumn{1}{l|}{1 s}  & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
   & \multicolumn{1}{l|}{5 s}  & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
   & \multicolumn{1}{l|}{10 s} & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
   & \multicolumn{1}{l|}{none} & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
\end{tabular}
\end{table}

The next table gathers the bounds linked to substitutions generation, the first one limits the number of monomorphising substitutions that are generated per clause during the final phase. The second one gives an absolute cap on the overall number of substitutions generated at each clause during the type argument generation.

\begin{table}[H]
\caption{Substitution generation}
\centering\begin{tabular}{@{}lc*{4}{>{\centering\arraybackslash}p{1.5em}}@{}}
   \toprule
   && \multicolumn{4}{c}{mono subst}\\
   && 2 & 5 & 7 & 10\\
   \cmidrule(lr){3-6}
   \multirow{4}{4.1em}{subst cap}
   & \multicolumn{1}{l|}{50}   & 0 & 0 & 0 & 0\\
   & \multicolumn{1}{l|}{100}  & 0 & 0 & 0 & 0\\
   & \multicolumn{1}{l|}{500}  & 0 & 0 & 0 & 0\\
   & \multicolumn{1}{l|}{none} & 0 & 0 & 0 & 0\\

@@

This last table attempts to determine which are the best bounds related to the depth at which the monomorphisation problem is run as well as how long zipperposition is allowed to run before monomorphisation (and the subsequent call of E) is ran.

\begin{table}[H]
% not super happy with caption
\caption{Problem depth}
\centering\begin{tabular}{@{}lc*{4}{>{\centering\arraybackslash}p{1.5em}}@{}}
   \toprule
   && \multicolumn{4}{c}{E call step}\\
   && 0 & 15 & 45 & 90\\
   \cmidrule(lr){3-6}
   \multirow{4}{3.3em}{loop nb}
   & \multicolumn{1}{l|}{2} & 0 & 0 & 0 & 0\\
   & \multicolumn{1}{l|}{3} & 0 & 0 & 0 & 0\\
   & \multicolumn{1}{l|}{4} & 0 & 0 & 0 & 0\\
   & \multicolumn{1}{l|}{5} & 0 & 0 & 0 & 0\\

@@

% We have two options, either use the current tables and make a tiered old/new test structure, or test everyting at once, which would be possible (32 options vs 16 with the tiered approach) however the results would most likely not be very pleasant to present, a highlight would have to be selected.

% final tests to make sure everything plays well together
\begin{table}[H]
\caption{Problem size refinement}
\centering\begin{tabular}{@{}llcccc@{}}
   \toprule
   && \multicolumn{4}{c}{substitution generation} \\
   && \multicolumn{2}{c}{old} & \multicolumn{2}{c}{new} \\
   \cmidrule(lr){3-4} \cmidrule(lr){5-6}
   && \multicolumn{2}{c}{problem depth} &\multicolumn{2}{c}{problem depth}\\
   && old & new & old & new \\
   \cmidrule(lr){3-4} \cmidrule(lr){5-6}
   \multirow{2}{7.5em}{clause generation}
   &\multicolumn{1}{l|}{old} & 0  & 0 & 0 & 0 \\
   &\multicolumn{1}{l|}{new} & 0  & 0 & 0 & 0\\
   \bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\caption{Type argument generation refinement}
\centering\begin{tabular}{@{}llcc@{}}
   \toprule
   && \multicolumn{2}{c}{mono bounds} \\
   && old & new\\
   \cmidrule(r){3-4}
   \multirow{2}{5.4em}{poly bounds}
   &\multicolumn{1}{l|}{old} & 0  & 0 \\
   &\multicolumn{1}{l|}{new} & 0  & 0 \\
   \bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\caption{Final bounds refinement}
\centering\begin{tabular}{@{}llcc@{}}
   \toprule
   && \multicolumn{2}{c}{type argument bounds} \\
   && old & new\\
   \cmidrule(r){3-4}
   \multirow{2}{5.4em}{problem size bounds}
   &\multicolumn{1}{l|}{old} & 0  & 0 \\
   &\multicolumn{1}{l|}{new} & 0  & 0 \\
   \bottomrule
\end{tabular}
\end{table}
